MSAD_PCA_Walkthrough

### 2017-07-07 README.Rmd
Updated Simulation_Vignette.Rmd because I hadn't looked at it in a while. This is to prepare for the pkgdown website build.

## Installation
Make sure you have the latest version of the `devtools` package, and pull the package from GitHub. Remember, if you can read this file, you are one of the few people who have access to this package. In addition, you can also run the following:
```{r packLoad_GitHub}
devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
```
where you create the value of "tokenHere" by generating a personal access token (PAT) at https://github.com/settings/tokens and copying the quoted string to this argument.

>>>>

## Installation
Make sure you have the latest version of the `devtools` package, and pull the package from GitHub. Remember, if you can read this file, you are one of the few people who have access to this package. In addition, you can also run the following:
```{r packLoad_GitHub, eval=FALSE}
devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
```
where you create the value of "tokenHere" by generating a personal access token (PAT) at https://github.com/settings/tokens and copying the quoted string to this argument.
Load the library after installation by
```{r packLoad}
library(mvMonitoring)
```
